---
title: ""
author: ""
date: ""
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(flextable)
```


<br>

<br>

#### **Type of file format supported in plotS**

 > It support comma separated file (csv), tab delimited (tsv) and excel sheet file (xls and xlsx)



#### **Must the input data be of only numeric columns?**

> No, data can be a combination of numerical and categorical variables.



#### **Why and when to reshape the data?**

> Reshaping is required depending on the input data so that variables can be compared. In order to represent and compare variables in plotS, the input data must be in **long format** rather than **wide format**. In the example below, _Table 1_ represents the wide format, while _Table 2_ represent the long format. You need to reshape your data if it is in wide format and want to compare between variables (control, treatment1 and treatment2).



_Example_


```{r}
table1 <- data.frame(sample = c( paste0(rep("sample", 3), 1:3) ), control = c(sample(20:50, 3)),
                     treatment1 = c(sample(10:40, 3)), treatment2 = c(sample(30:60, 3)))
# knitr::kable(table1

table1 %>% flextable() %>% autofit() %>% 
add_header(., sample = "Table 1. Typical data with wide format.", top = TRUE) %>%
  merge_at(., i = 1, j = 1:ncol(table1), part = "header") %>%
    align(., i = 1, j = 1:ncol(table1), align = "center", part = "header")

```

<br>
<br>
_Data in the table 1, which is in a wide format, reshaped to long format in table 2._

<br>

```{r}
table2 <- pivot_longer(table1, cols = !sample, names_to = "treatments", values_to = "value")

table2 %>% flextable() %>% autofit() %>% 
add_header(., sample = "Table 2. Data in table 1 reshaped to long format.", top = TRUE) %>%
  merge_at(., i = 1, j = 1:ncol(table2), part = "header") %>%
    align(., i = 1, j = 1:ncol(table2), align = "center", part = "header")

```

<br>


#### **What is aesthetic option?**

> Aesthetic options mapped the variables to visual properties - color, shape or line type. It let user customize the visual properties and differentiate between variables. 


#### **How was effect size estimated?**

> Effect size is estimated using different methods based on the statistical test applied.


> - T-test: cohen's d of rstatix package is used for the test.

> - ANOVA : partial eta squared from effectsize package

> - wilcoxon test: the effect size is measured as `z` statistic, derived from the wilcoxon test, divided by square root of the sample size. It is implemented using rstatix package. 

> - Kruskal-Wallis test: measured as eta squared based on H-statistic derived from the Kruskal-Wallis test. It is given as `eta2[H] = (H - k + 1)/(n - k)`. Where, `k` is the number of groups and `n` is the total number of observations. It is implemented using rstatix package.


#### **R packages used for the application**

- [ggplot2](https://ggplot2.tidyverse.org/) : most of the graphics in this app are created using ggplot2.

- [rstatix](https://cran.r-project.org/web/packages/rstatix/index.html) : most of the statistical methods in the app use this pipe-friendly package.

- [rmarkdown](https://rmarkdown.rstudio.com/) : creating documents for report.


- [shiny](https://shiny.rstudio.com/) : building the interactive web apps.

- [tidyverse](https://www.tidyverse.org/) : collection of R packages for data science.

- other packages:
    - [car](https://cran.r-project.org/web/packages/car/index.html), [coin](https://cran.r-project.org/web/packages/coin/index.html), [data.table](https://cran.r-project.org/web/packages/data.table/index.html), [DT](https://rstudio.github.io/DT/), [effectsize](https://cran.r-project.org/web/packages/effectsize/index.html), [flextable](https://cran.r-project.org/web/packages/flextable/index.html), [ggpubr](https://cran.r-project.org/web/packages/ggpubr/index.html), [glue](https://glue.tidyverse.org/),  [MASS](https://cran.r-project.org/web/packages/MASS/index.html), [memoise](https://memoise.r-lib.org/), [multcompView](https://cran.r-project.org/web/packages/multcompView/index.html), [openxlsx](https://ycphs.github.io/openxlsx/), [reactable](https://glin.github.io/reactable/), [readxl](https://readxl.tidyverse.org/), [rlang](https://rlang.r-lib.org/),  [shinydashboard](https://rstudio.github.io/shinydashboard/), [shinyWidgets](https://shinyapps.dreamrs.fr/shinyWidgets/), [skimr](https://github.com/ropensci/skimr), [svglite](https://www.tidyverse.org/blog/2021/02/svglite-2-0-0/), [vroom](https://www.tidyverse.org/blog/2019/05/vroom-1-0-0/).




