---
title: ""
author: ""
date: ""
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(flextable)
```


<br>

<br>

#### **Type of file format supported in plotS**

 It support comma separated file (csv), tab delimited (tsv) and excel sheet file (xls and xlsx)

<br>

#### **Must the input data be of only numeric columns?**

No, data can be a combination of numeric and categorical variables.

<br>


#### **Why and when to reshape the data?**

<!-- Depending on the input data, reshape is necessary so that comparison can be made between variables. Graphics in plotS is drawn using [Ggplot2](https://ggplot2.tidyverse.org/). To represent and compare between variables in ggplot require the input data in long format rather than wide format (example below). Table 1 represents wide format and table 2 represents long format.  -->

Reshaping is required depending on the input data so that variables can be compared. In order to represent and compare variables in plotS, the input data must be in **long format** rather than **wide format**. In the below example, _Table 1_ shows the wide format, while _Table 2_ represent the long format. You need to reshape your data if it is in wide format and want to compare between variables (control, treatment1 and treatment2).
<!-- PlotS graphics are created with [Ggplot2](https://ggplot2.tidyverse.org/), so it inherit the same property.  -->

_Example_


```{r}
table1 <- data.frame(sample = c( paste0(rep("sample", 3), 1:3) ), control = c(sample(20:50, 3)),
                     treatment1 = c(sample(10:40, 3)), treatment2 = c(sample(30:60, 3)))
# knitr::kable(table1

table1 %>% flextable() %>% autofit() %>% 
add_header(., sample = "Table 1. Typical data with wide format.", top = TRUE) %>%
  merge_at(., i = 1, j = 1:ncol(table1), part = "header") %>%
    align(., i = 1, j = 1:ncol(table1), align = "center", part = "header")

```

<br>
<br>
_Data in the table 1, which is in a wide format, reshaped to long format in table 2._

<br>

```{r}
table2 <- pivot_longer(table1, cols = !sample, names_to = "treatments", values_to = "value")

table2 %>% flextable() %>% autofit() %>% 
add_header(., sample = "Table 2. Data in table 1 reshaped to long format.", top = TRUE) %>%
  merge_at(., i = 1, j = 1:ncol(table2), part = "header") %>%
    align(., i = 1, j = 1:ncol(table2), align = "center", part = "header")

```

<br>


#### **What is aesthetic option?**

Aesthetic options mapped the variables to visual properties - color, shape or line type. It let user customize the visual properties as well as differentiate between variables. 

