---
title: ""
author: ""
date: ""
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(flextable)
```


<br>

<br>

#### **Type of file format supported in plotS**

 > It support comma separated file (csv), tab delimited (tsv) and excel sheet file (xls and xlsx)



#### **Must the input data be of only numeric columns?**

> No, data can be a combination of numerical and categorical variables.



#### **What is long and wide format, and why to reshape it?**


> Each independent variable forms a column in **wide format**, and each cell or data point in the column is a record of dependent variable (table 1). In other words, each row is a mix of records of dependent value of all the independent variables. In contrast, independent and dependent variables are organised into different columns in **long format**, with each row representing the record of one independent variable (table 2). Arranging the data in long format allow comparisons between the independent variables in PlotS. It can further represent more independent variables, if present, in the graph using aesthetic options. To represent and compare variables in PlotS, reshaping to long format is required and recommended.


<!-- > Reshaping is required depending on the input data so that variables can be compared. In order to represent and compare variables in plotS, the input data must be in **long format** rather than **wide format**. In the example below, _Table 1_ represents the wide format, while _Table 2_ represent the long format. You need to reshape your data if it is in wide format and want to compare between variables (control, treatment1 and treatment2). -->



_Example : the data is a comparison of yield, measured as dried weight of plants, obtained under control and two different treatment conditions. The given three growth conditions are the independent variables and yield is the dependent variable._


```{r}
table1 <- data.frame(sample = c( paste0(rep("sample", 3), 1:3) ), control = c(sample(20:50, 3)),
                     treatment1 = c(sample(10:40, 3)), treatment2 = c(sample(30:60, 3)))
# knitr::kable(table1

table1 %>% flextable() %>% autofit(add_w = 1) %>% 
add_header(., sample = "Table 1. Wide format table. Each independent variable forms the column and each cell is the record of dependent variable i.e. yield.", top = TRUE) %>%
  merge_at(., i = 1, j = 1:ncol(table1), part = "header") %>%
    align(., i = 1, j = 1:ncol(table1), align = "center", part = "header")

```

<br>
<br>
_Data in the table 1, which is in a wide format, reshaped to long format in table 2._

<br>

```{r}
table2 <- pivot_longer(table1, cols = !sample, names_to = "treatments", values_to = "value")

table2 %>% flextable() %>% autofit(add_w = 1.5) %>% 
add_header(., sample = "Table 2. Long format table. Independent variables (control, treatment1 and treatment2) are organised in the 'treatments' column and dependent variable (yield) is placed under 'value' column.", top = TRUE) %>%
  merge_at(., i = 1, j = 1:ncol(table2), part = "header") %>%
    align(., i = 1, j = 1:ncol(table2), align = "center", part = "header")

```

<br>


#### **What is aesthetic option?**

> Aesthetic options mapped the variables to visual properties - color, shape or line type. It let user customize the visual properties and differentiate between variables. 

#### **What is the statistical methods used for conducting normality test?**


> In PlotS, we used Shapiro-Wilk's test if the sample size is less than 5000, otherwise, Kolmogorov-Smirnov's test is used.


#### **Estimating the effect size**

> Effect size is estimated using different R packages.


> - We used **effectsize** package of R to estimate the effect size of _T-test_ and _ANOVA_.


> - **rstatix** package is used for measuring the effect size of _Wilcoxon_ and _Krukal-Wallis tests_.


#### **Does the app save user data?**

> No, after the session ends, all data is deleted.


#### **R packages used for the application**

- [ggplot2](https://ggplot2.tidyverse.org/) : most of the graphics in this app are created using ggplot2.

- [rmarkdown](https://rmarkdown.rstudio.com/) : creating documents for report.

- [rstatix](https://cran.r-project.org/web/packages/rstatix/index.html) : most of the statistical methods in the app use this pipe-friendly package.

- [shiny](https://shiny.rstudio.com/) : building the interactive web apps.

- [tidyverse](https://www.tidyverse.org/) : collection of R packages for data science.

- other packages:
    - [car](https://cran.r-project.org/web/packages/car/index.html), [coin](https://cran.r-project.org/web/packages/coin/index.html), [data.table](https://cran.r-project.org/web/packages/data.table/index.html), [DT](https://rstudio.github.io/DT/), [effectsize](https://cran.r-project.org/web/packages/effectsize/index.html), [flextable](https://cran.r-project.org/web/packages/flextable/index.html), [ggforce](https://ggforce.data-imaginist.com/), [ggpp](https://cran.r-project.org/web/packages/ggpp/index.html), [ggpubr](https://cran.r-project.org/web/packages/ggpubr/index.html), [ggside](https://github.com/jtlandis/ggside), [glue](https://glue.tidyverse.org/), [MASS](https://cran.r-project.org/web/packages/MASS/index.html), [memoise](https://memoise.r-lib.org/), [multcompView](https://cran.r-project.org/web/packages/multcompView/index.html), [openxlsx](https://ycphs.github.io/openxlsx/), [reactable](https://glin.github.io/reactable/), [readxl](https://readxl.tidyverse.org/), [rlang](https://rlang.r-lib.org/), [scales](https://cran.r-project.org/web/packages/scales/index.html), [shiny.router](https://github.com/Appsilon/shiny.router), [shinyalert](https://github.com/daattali/shinyalert), [shinyBS](https://ebailey78.github.io/shinyBS/), [shinydashboard](https://rstudio.github.io/shinydashboard/), [shinyjqui](https://cran.r-project.org/web/packages/shinyjqui/vignettes/introduction.html), [shinyjs](https://cran.r-project.org/web/packages/shinyjs/vignettes/shinyjs.html), [shinyWidgets](https://shinyapps.dreamrs.fr/shinyWidgets/), [skimr](https://github.com/ropensci/skimr), [svglite](https://www.tidyverse.org/blog/2021/02/svglite-2-0-0/), [vroom](https://www.tidyverse.org/blog/2019/05/vroom-1-0-0/).




