---
title: "PlotS: web-based application for data analysis and visualization"
subtitle: "Statistical analysis summary"
author: ''
date: ''
output: pdf_document
params:
  table1: NA
  table2: NA
  caption: NA
  table3: NA
  table4: NA
  subcaption: NA
---
```{r setup, include=FALSE, echo=FALSE} 
knitr::opts_chunk$set(echo = FALSE)
```

**_Note_: For transparency and credibility of your research analysis, always report the statistical method and a description of its appropriateness for the data. Record the result in accepted scientific standard, not just p-value. Report effect size in addition to p-value.** 


# Table 1. Summary of the input data
```{r}
params$table1
```
# Table 2. Descriptive statistics
```{r}
knitr::kable(params$table2)
```

# Table 3. Summary for t-test (`r if(params$caption == "welch"){"Welch's test"}else{"Student's test"} `).

'.y.' is the variable used in y-axis; 'group 1 & 2' are the groups compared in the test; 'n' are the sample counts; 'statistic' is the test used to compute the p-value; 'p' is the p-value
```{r }
knitr::kable(params$table3)
```

# Table 4. Table of effect size. Measures the strength of relationship between variables.

`r params$subcaption`
```{r}
knitr::kable(params$table4)

```

