---
title: "PlotS: web-based application for data analysis and visualization"
subtitle: "Statistical analysis summary"
author: ''
date: ''
output: pdf_document
params:
  anovaType: NA
  model: NA
  table1: NA
  table2: NA
  table3: NA
  table4: NA
  table5: NA
  figure1: NA
  figure2: NA
  figure3: NA
  statment1: NA
  statment2: NA
---
```{r setup, include=FALSE, echo=FALSE} 
knitr::opts_chunk$set(echo = FALSE)
par(mfrow = c(1,3))
```


**_Note_: For transparency and credibility of your research analysis, always report the statistical method and a description of its appropriateness for the data. Record the result in accepted scientific standard, not just p-value. Report effect size in addition to p-value.** 


# Table 1. Summary of the input data
```{r echo=FALSE}
params$table1
```
# Table 2. Descriptive statistics
```{r echo=FALSE}
knitr::kable(params$table2)
```

# Testing assumptions for the parametric test
```{r echo=FALSE, fig.width=4, fig.height=4}
params$figure1

params$figure2

params$figure3

```

The p-value (rounded to 3 decimal places) for Levene's homoscedasticity test is `r params$statment1`, and Kolmogrov-Smirnov's normality test is `r params$statment2`.


**Note: Higher the p-value (generally greater than 0.05), the more likely it satisfy the parametric assumptions.**


# Table 3. Summar for `r if(params$anovaType == "one"){"one-way ANOVA"}else{"two-way ANOVA"} ` `r if(params$model == "additive"){"(additive model)"}else if(params$model == "non-additive"){"(non-additive model)"}`.
```{r echo=FALSE}
knitr::kable(params$table3)
```

# Table 4. Table of effect size. Measures the strength of relationship between variables.

Eta2 is the Generalized eta squared (Eta2); CI is the confidence interval; CI_low and CI_high are the upper and lower bound.
```{r echo=FALSE}
knitr::kable(params$table4)

```

# Table 5. Post-hoc analysis using Tukey's Honest Significant Difference method
```{r}
if(params$anovaType == "one"){
  knitr::kable(params$table5)
}else{
  params$table5
}
```


